Learning filters from user provided image makers

### 2020-06-01 main.tex
add results with SVM

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
  Ours & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.85 \pm 0.02$\\
  Ours (fine tuned) & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.84 \pm 0.02$\\
  VGG-16 & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  VGG-16 (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}

>>>>

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
  Ours & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.85 \pm 0.02$\\
  Ours (fine tuned) & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.84 \pm 0.02$\\
  Ours with SVM & $0.81 \pm 0.02$ & $0.77 \pm 0.03$ & $0.78 \pm 0.02$\\
  VGG-16 & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  VGG-16 (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}
